This blueprint proves part of the bound for merkle tree soundness

Proof outline.

Decompose the joint event by whether the committed `root` appears as the
output of any hash query in committingAdv's log:

Case A — `root ∈ committingLog.outputs`.
  Under no-collision, committingAdv's query producing `root` is the *unique*
  combined-log query producing it, so any chain reaching `root` must use that
  exact input pair. Inducting down the tree from `root`, the verifier's level-`k`
  query input must agree with committingAdv's level-`k` query (for k = s.depth,
  …, 1): if it did not, the verifier's level-`k` output would either equal the
  extracted node value at that position (forcing input agreement by no-collision)
  or differ (breaking the chain to `root`). By induction the verifier's chain
  traces exactly the path `extractor` builds, so opened (leaf, proof) equals
  extracted (leaf, proof) and the win condition fails. Hence
  `Pr[case A ∧ no-collision ∧ win] = 0`.

Case B — `root ∉ committingLog.outputs`.
  Then `extractor s queryLog root` returns the all-`none` extension below the
  root, so the leaf-mismatch disjunct of `adversary_wins_extractability_game_event`
  is automatic whenever `idx.depth > 0`, reducing the win event to
  `verified = true`. Verification succeeding requires the random oracle to produce
  `root` at the verifier's terminal hash query. Since by case hypothesis no prior
  committingAdv query produced `root`, that terminal output is uniform on `α`
  (conditional on its input pair being fresh, which no-collision guarantees up to
  duplicate-query reuse), so it equals `root` with probability `1/|α|` per chain.

Step 4 (union bound).
  Sum `1/|α|` over `idx : SkeletonLeafIndex s` (≤ `s.leafCount` choices) and the
  ≤ `s.depth + 1` levels at which the verifier's chain may "rejoin" committingAdv's
  tree from below; the factor of `2` absorbs the left/right child direction at
  each rejoin.

Formalization sketch.
  1. Express the event as a finite disjunction over `(idx, k)` with
      `k : Fin (s.depth + 1)` indexing the deepest level at which the verifier's
      chain leaves committingAdv's tree.
  2. For each `(idx, k)`, bound the per-event probability by `1 / |α|` using the
      random oracle's fresh-output uniform bound (`probOutput_query` /
      `evalDist_query`).
  3. Sum via `probEvent_finset_sum_le` and a `Fintype.card`-style cardinality
      bound on `SkeletonLeafIndex s` (≤ `s.leafCount`) to assemble the stated
      `2 * (s.depth + 1) * s.leafCount / |α|` bound.